\documentclass[draft]{article}

\usepackage{amssymb}
\usepackage{amstext}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, urlcolor=blue, pdfborder={0 0 0}]{hyperref}
\usepackage{verbatim}

\tolerance=500
\newcommand*{\urldecorated}[1]{[\url{#1}]}

\newlength{\firstcolwidth}

\newcommand*{\secondcolindent}[3][2em]{
\par
{
\parindent=#1
\settowidth{\firstcolwidth}{#2}
\addtolength{\firstcolwidth}{#1}
\setlength{\hangindent}{\firstcolwidth}
#2#3
\par
}
}

\newcommand*{\ProgramInvokation}[2]{
\secondcolindent[2em]{\texttt{java -cp ape.jar \mbox{ru.autosome.#1} }}{\texttt{#2}}
}

\newcommand*{\DefineProgramInvokationCommand}[2]{
\newcommand{#1}[1]{
\ProgramInvokation{#2}{##1}
}
}

\DefineProgramInvokationCommand{\EvalSimilarity}{macroape.EvalSimilarity}
\DefineProgramInvokationCommand{\ScanCollection}{macroape.ScanCollection}
\DefineProgramInvokationCommand{\FindThreshold}{ape.FindThreshold}
\DefineProgramInvokationCommand{\FindPvalue}{ape.FindPvalue}
\DefineProgramInvokationCommand{\PrecalculateThresholds}{ape.PrecalculateThresholds}
\DefineProgramInvokationCommand{\SNPScan}{perfectosape.SNPScan}


\newcommand*{\example}[1]{\par\vspace{2ex}\noindent\textbf{Example#1:}\par\nopagebreak\vspace{0.5ex plus 0.3ex minus 0.1ex}}
\newcommand*{\exampleof}[1]{\example{ (#1)}}
\newcommand*{\usageheader}[1][Usage]{\par\noindent\textbf{#1:}\par\nopagebreak}
\newcommand*{\outputheader}[1][Output]{\par\noindent\textbf{#1:}\par\nopagebreak}
\newcommand*{\cmdoutput}[1]{{\small#1}}
\newcommand*{\cmdoutputfromfile}[1]{\cmdoutput{\verbatiminput{./ProgramOutput/#1}}}


\newcommand*{\inangles}[1]{\textless#1\textgreater}
\newcommand*{\requiredarg}[1]{\inangles{#1}}
\newcommand*{\optionalarg}[1]{[#1]}
\newcommand*{\cmdname}[1]{\mbox{\texttt{#1}}}
\newcommand*{\cmdoption}[1]{\mbox{\texttt{#1}}}

\newcommand*{\pvalue}{\mbox{P-value}}
\newcommand*{\pvalues}{\mbox{P-values}}

\begin{document}

\title{
MACRO-PERFECTOS-APE~---\\{\small MAtrix CompaRisOn \&\\ Predicting Regulatory Functional Effect of SNPs\\ by Approximate \pvalue\ Estimation}\\
-- User Manual --
}
\maketitle

\input{sections/abstract}

\input{sections/technical-notes}

\input{sections/overview}
\input{sections/command-line-format}

\section{Basic APE tools}
\input{sections/ape-introduction}

\input{sections/tools/FindThreshold}
\input{sections/tools/FindPvalue}
\input{sections/tools/PrecalculateThresholds}


\section{MACRO-APE: Matrix Comparison by Approximate P-value Estimation}
\input{sections/macroape-introduction}

\input{sections/tools/EvalSimilarity}
\input{sections/tools/ScanCollection}


\section{PERFECTOS-APE: Predicting Regulatory Functional Effect of SNPs by Approximate P-value Estimation.}
\input{sections/perfectosape-introduction}

\input{sections/tools/SNPScan}


\section{Data formats}
% Augment with information about transposed matrices with a link to options
\input{sections/formats/position-matrix-format}
\input{sections/formats/perfectosape-input}


\section{Additional command-line options}
\input{sections/options/options-introduction}

\input{sections/formats/dinucleotide-matrix-format}

% Here we should insert some link to pcm-pwm conversions
\input{sections/options/transposition}

\input{sections/formats/background-format}
\input{sections/formats/dibackground-format}

\input{sections/options/advanced-options}


\section{Formal math}
  \input{sections/discretization-strategy}
  \input{sections/options/pcm-ppm-pwm-conversion-format}

\section*{References}
[MACROAPE] Algorithms Mol Biol. 2013, 8:23.
Jaccard index based similarity measure to compare transcription factor binding site models.
Ilya E Vorontsov, Ivan V Kulakovskiy and Vsevolod J Makeev

[Touzet2007] Algorithms Mol Biol. 2007 Dec 11;2:15. Efficient and accurate \pvalue  
computation for Position Weight Matrices. Touzet H, Varré JS.

[Pape2008] Bioinformatics. 2008 Feb 1;24(3):350-7. Epub 2008 Jan 2. Natural similarity 
measures between position frequency matrices with an application to clustering. Pape UJ, 
Rahmann S, Vingron M.

[Lifanov2003] Genome Res. 2003 Apr;13(4):579-88. Homotypic regulatory clusters in 
Drosophila. Lifanov AP, Makeev VJ, Nazina. AG, Papatsenko DA.
\end{document}
