\subsubsection{ScanCollection}
This tool uses a collection of motifs to find PWMs similar to a given query. The tool returns 
a list of all PWMs in the collection with corresponding similarity levels comparing to the query 
PWM. List is sorted by similarity in descending order so the PWMs similar to the query are 
located at the top of the list.
\emph{FIX: Actually not yet sorted}


NOTE! The shift and orientation are reported for PWMs from the collection relative to the query 
PWM.

\example{(search for motifs similar to \texttt{KLF4\_f2}, HOCOMOCO collection with uniform background), should take $\sim$1-2 minutes}
\ScanCollection{motifs/KLF4\_f2.pat\\ ./hocomoco\_ad\_uniform/}
% \outputheader[Output (STDOUT)]
% \cmdoutputfromfile{ScanCollectionOutput(KLF4,default).txt}

\emph{FIX: \cmdoption{--precise} has required parameter, not optional, yet}

One can also use the two-pass search mode when the top of the list is additionally 
reprocessed using a more precise discretization level. Second pass is executed only 
if \cmdoption{--precise [min\_similarity=0.01]}
key is specified. The precise search will recheck only the PWMs 
similar to the query with a similarity no less than \cmdoption{min\_similarity}. The results of the second pass 
will be marked by asterisk(*) in the output.

One can specify similarity cutoff with option \cmdoption{-c \requiredarg{similarity cutoff}} to discard 
comparison results with the resulting similarity less than a given value. By default results with similarity less than 0.05 are discarded.
In order to print comparison results for all PWMs in collection, one should specify \cmdoption{--all} option.

\example{(search PWMs similar to \texttt{KLF4\_f2}, uniform normalization, extended precision for the most similar PWMs), should take $\sim$10 seconds for 1.5 GHz CPU}
\ScanCollection{motifs/KLF4\_f2.pat\\ ./hocomoco\_ad\_uniform/\\ --precise}
% \outputheader[Output (STDOUT)]
% \cmdoutputfromfile{ScanCollectionOutput(KLF4,precise).txt}

To find similar PWMs using a particular \pvalue\ level one should use the \cmdoption{"-p"}~option.

\exampleof{should take $\sim$7 seconds for 1.5GHz CPU}
\ScanCollection{motifs/KLF4\_f2.pat\\ ./hocomoco\_ad\_uniform/\\ -p 0.001\\ -c 0.06 --precise 0.1}
% \outputheader[Output (STDOUT)]
% \cmdoutputfromfile{ScanCollectionOutput(KLF4,CustomPvalue,CustomFilters).txt}
