Each tools can be configured with multiple options. All options should go after the required arguments. There are some options common for the majority of MACRO-PERFECTOS-APE tools and some options are tool specific. Tool-specific options were already described in the Tools section. Common options will  be described in this section.

Options can be divided into two large classes: those which alter input data format and those which affect tool calculation. The first class of options allows one to load motifs from PCM or PPM instead of PWM, read matrices in non-standard transposed format and make mononucleotide motifs mimic dinucleotide ones. The second class of options allow specifing background model, select \pvalue\ evaluation mode, limit memory consumption and so on.

Some tools have multiple options correspondning to the same option type. In such cases this manual describes the only one option from the family. This manual doesn't describe each of options separately and doesn't try to list all the options the tool. For a full list of tool options, please use \cmdoption{--help} command line option.

\subsection{Option families}
{\small
Families of options have similar names, but different prefices. For example \cmdname{macroape.di.EvalSimilarity} tool, has an option \cmdoption{--from-mono}. This option means that both dinucleotide motifs should be obtained from mononucleotide ones. In turn \cmdoption{--first-from-mono} options means that the first motif will be obtained from mononucleotide input. \cmdoption{--second-from-mono} does the same but for the second motif.

Analogous options for \cmdname{macroape.ScanCollection} are named \cmdoption{--query-from-mono} and \cmdoption{--collection-from-mono}. Option \cmdoption{--query-from-mono} demands mononucleotide query motif, and \cmdoption{--collection-from-mono} means that each motif in collection should be loaded from mononucleotide motif. The same is appliable for options like \cmdoption{--background}.

Such triples of options are typically listed in the help string like this: \cmdoption{--[first-|second-]from-mono}. It means that one can use both prefixed and non-prefixed options. And possible prefixes are given in square brackets separated with a pipe sign \texttt{"|"}.

\textbf{Note:} Be careful! Prefixed options are always written in a long form. One can use both \cmdoption{-b} and \cmdoption{--background} as synonymous but even if \cmdoption{--first-background} is available there is no \cmdoption{--first-b} option.

\textbf{Note:} Existence of separate options for each motif doesn't necessarily involve existence of common option. E.g. \cmdname{macroape.EvalSimilarity} has options \cmdoption{--first-threshold} and \cmdoption{--second-threshold} but doesn't have \cmdoption{--threshold} because it has no sense.
}
